%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Detta är ett exempel på ett latexdokument.
% 
% Alla dokument består av följande delar:
%
%          \documentclass[optioner]{dokumentklass}
%            ...inställningar...
%          \begin{document}
%            ...text...
%          \end{document}
%
% Som ni kanske redan har förstått är används procent (%) för
% kommentarer.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper]{article}

\usepackage{listings}
\usepackage[T1]{fontenc}                % För svenska bokstäver
\usepackage[swedish]{babel}             % För svensk avstavning och svenska
                                        % rubriker (t ex "innehållsförteckning)
\title{Programming Project, Database Technology}
\author{Tim Dolck dat11tdo@student.lu.se \\ 
Julian Kroné dat11jkr@student.lu.se \\
Christopher Nilsson dat11cni@student.lu.se}
%\date{}           % Blir dagens datum om det utelämnas

\begin{document}

\maketitle                      % Skriver ut rubriken som vi
                                % deklarerade ovan med \title, \author
                                % och eventuellt \date
\newpage
\section{Introduction}          % Detta kommando gör en rubrik

\section{Requirements}

Krusty Cookies database system is built with the simplest possible interface to make sure all employees are able to use it. 
The system is also very stable and the bugs are very few. 

At this point the system is only a test system with all aspects of production implemented although the database is prepared for future development!
So far the system can be used to search/filter pallets, create pallets and block pallets.
When a pallet is created the database of rawmaterials is updated according to the cookietype of the pallet created.
When searching/filtering pallets several parameters can be used such as id-number, production time and status. 

\section{Outline}

\section{Model}

\section{Statements}

\section{Manual}

\subsection{Starting the program}
The system is delivered as a compressed zip file.
To decompress it use the built-in decompress features in your operating system of choice.
\paragraph{Example:}
On a unix system run the following command:
\begin{lstlisting}[frame=single]  % Start your code-block

> unzip krusty.zip
\end{lstlisting}

To run the system Java and Typesafe Reactive Platform is used. If you don't have them installed, install them now.
Inside your unzipped folder there is a folder named bin. Go there.
To run the program type the following:
\paragraph{Unix:}

\begin{lstlisting}[frame=single]  % Start your code-block

> ./db-project
\end{lstlisting}

\paragraph{Windows:}

\begin{lstlisting}[frame=single]  % Start your code-block

> db-project.bat
\end{lstlisting}

\end{document}                 % The input file ends with this command.
